\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\label{ch:acknowledgments}

There are a great number of people without whom this thesis
would not be possible.

First, I would like to thank my thesis advisor, David Grier. David has been
an incredible and patient mentor throughout my graduate career.
He has fostered his own community of graduate and undergraduate
students, all of whom were enticed by his exuberance and stayed for
his guidance. He is a very creative spirit and I hope that after
all these years of working together, I have in part acquired his eye for detail.
I will not soon forget his cheerful grin, particularly on those
most productive days when he was clinching his teeth and muttering
mild expletives to himself.

Members of the Grier group, Grierlings as they are known, are
particularly precious to me. I am thankful for the overlap I shared
with Lisa, Bhaskar, David, Henrique, Olawale, Chen, Aaron,
Argha, Jordan, Mohammed, and Lauren. There are countless
undergraduates and high school students who have come
and gone during my tenure, so I will simply say thank you all for
your enthusiasm and willingness to learn. Should the battle of the
research groups ever arise, I will most certainly have your backs.

I must thank my classmates from room 639 of Meyer Hall:
Ali, Chang, Chen, Cato, Christine (Xtine), Doycho, Geoff, Hossein,
Jie, Kilian, Mohammadjavad (MJ), Nityasri (Nitya), Ruben, Xiaoyi,
Yike, Yin, Yu-Ming, and Yuqian. I appreciate that you were all
receptive to meeting and engaging with a ``middle-of-Amurica''
white guy. With any amount of luck, we have at least one
more round of Werewolves left to play.

I especially would like to thank the ``Dream Team'' of my year:
Christine, Doycho, Kilian and Nitya. While we may be the last of our
year to graduate, we did not drink the least.

Traveling to conferences is one of the more exciting and, at
times, stressful aspects of graduate life. I am incredibly grateful
for my friendships with Etienne Ducrot, Melissa Ferrari, and Christine
Middleton, which were forged on a March Meeting trip
to San Antonio, Texas. Sure, a matinee showing of ``50 Shades of Grey''
was a very unlikely start but the depth of our friendship has proven to
be equally as rare.

Finally, thank you to my family whose unconditional love and repeated
phone calls make it impossible for me to not feel adored. Thank you so
much for encouraging my geekiness as a child even when my excitement
wasn't mutual. You created space for me to be me and it has made all
the difference in my life.
